---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
pkgload::load_all(export_all = FALSE)
```

# shikakusphere

<!-- badges: start -->
<!-- badges: end -->

shikakusphere is a collection of miscellaneous funcitons for Japanese mahjong that wraps C++ sources of [cmajiang](https://github.com/TadaoYamaoka/cmajiang).

The name "shikakusphere" is a compound word of "shikaku" + "sphere". "shikaku" means "square" in Japanese.
It comes from "Shikakui Uchuu De Matteru Yo", which is the third ED of the anime "Saki", and sounds exactly like mahjong games.

## Installation

You can install the development version of shikakusphere from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("paithiov909/shikakusphere")
```

## Example

手牌（`hands`）は[kobalab/majiang-core](https://github.com/kobalab/majiang-core)の記法で表現する。

- [牌 · kobalab/majiang-core Wiki](https://github.com/kobalab/majiang-core/wiki/%E7%89%8C)
- [面子 · kobalab/majiang-core Wiki](https://github.com/kobalab/majiang-core/wiki/%E9%9D%A2%E5%AD%90)
- [牌姿 · kobalab/majiang-core Wiki](https://github.com/kobalab/majiang-core/wiki/%E7%89%8C%E5%A7%BF)

```{r}
hands <- c(
  "p222345z1234567",
  "p11222345z12345",
  "m055z7z7,m78-9,z5555,z666=",
  "m055z77,m78-9,z5555,z666=,",
  "m123p055s789z1117*"
)

# シャンテン数
n_xiangting <- calc_xiangting(hands)

# 有効牌（シャンテン数が減る牌）
# すでにテンパイしている or 和了形である場合、エラーになる
collect_tingpai(hands[n_xiangting > 0])

# 得点. この関数はvectorizeされていないので注意！
# baopaiはドラ表示牌、libaopaiは裏ドラ表示牌
score <- calc_defen(hands[n_xiangting == -1][1], baopai = "z1", libaopai = "")
score

# ロン和了のときはこんなふうに書く
calc_defen("m345567p234s3378", baopai = "z1", libaopai = "", rongpai = "s9=")

# あがり役の表示
parse_hupai(score$hupai, "jp")

# 牌姿を表示する
hand2img(score$shoupai[1])
```

# License

MIT
