---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
pkgload::load_all(export_all = FALSE)
```

# shikakusphere

<!-- badges: start -->
[![shikakusphere status badge](https://paithiov909.r-universe.dev/badges/shikakusphere)](https://paithiov909.r-universe.dev/shikakusphere)
[![R-CMD-check](https://github.com/paithiov909/shikakusphere/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/paithiov909/shikakusphere/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

shikakusphere is a collection of miscellaneous funcitons for Japanese mahjong that wraps C++ sources derived from [tomohxx/shanten-number](https://github.com/tomohxx/shanten-number) and [TadaoYamaoka/cmajiang](https://github.com/TadaoYamaoka/cmajiang).

The name "shikakusphere" is a compound word of "shikaku" + "sphere". "shikaku" means "square" in Japanese.
It comes from "Shikakui Uchuu De Matteru Yo", which is the third ED of the anime "Saki", and sounds exactly like mahjong games.

## Installation

You can install the development version of shikakusphere from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("paithiov909/shikakusphere")
```

## Example

手牌（`hands`）は[kobalab/majiang-core](https://github.com/kobalab/majiang-core)の記法で表現する。

**参考**

- [牌 · kobalab/majiang-core Wiki](https://github.com/kobalab/majiang-core/wiki/%E7%89%8C)
- [面子 · kobalab/majiang-core Wiki](https://github.com/kobalab/majiang-core/wiki/%E9%9D%A2%E5%AD%90)
- [牌姿 · kobalab/majiang-core Wiki](https://github.com/kobalab/majiang-core/wiki/%E7%89%8C%E5%A7%BF)
- [電脳麻将のプログラム中の中国語一覧 - koba::blog](https://blog.kobalab.net/entry/20170722/1500688645)

```{r}
library(shikakusphere)

hands <- c(
  "p222345z1234567",
  "p11222345z12345",
  "m055z7z7,m78-9,z5555,z666=",
  "m123p055s789z1117*"
)

# シャンテン数
n_xiangting <- calc_xiangting(hands)
n_xiangting

# 有効牌（シャンテン数が減る牌）
collect_tingpai(hands[n_xiangting >= 0])

# 得点. この関数はvectorizeされていないので注意！
# baopaiはドラ表示牌、libaopaiは裏ドラ表示牌
score <- calc_defen(hands[n_xiangting == -1][1], baopai = "z1")
score

# ロン和了のときはこんなふうに書く
calc_defen("m345567p234s3378", baopai = "z1", rongpai = "s9=")

# あがり役の表示
parse_hupai(score$hupai, "jp")

# 牌姿を表示する
hand2img(score$shoupai[1])
```

# License

GPL (>= 3). This package contains the [tinyxml2](https://github.com/leethomason/tinyxml2) code released under the zlib license.
